---
title: "Simulations"
output: html_document
---

# Simulations

# Round 1: 100 simulations, 1000 permutations per simulation

```{r sim1, echo=FALSE, message=FALSE}
source("./code/plotResults.R")

# load results files
resultsFiles <- grep("noidr", list.files("./data"), value=T)
for(x in resultsFiles) { load(paste0("./data/", x)) }
```

Parameters: 

* proportion differentially expressed in drug signature (p1): 0.05
* proportion differentially expressed in disease signature (p2): 0.05
* proportion differentially expressed in same direction (p3): 0, 0.5, 1
* proportion differentially expressed in different direction (p4): 0, 0.5, 1

Statistics: GSEA, IDR correlation, Spearman correlation, truncated Spearman correlation

Figure legends:

* Blue histogram: permutation statistics

* Red dots: simulation statistics

* Green violin plots: simulation p-values
  
```{r sim1Plots, echo=FALSE, message=FALSE, fig.cap=""}
plotResults(p1_0.05_p2_0.05_p3_0_p4_0)
plotResults(p1_0.05_p2_0.05_p3_0_p4_0.5)
plotResults(p1_0.05_p2_0.05_p3_0.5_p4_0)
plotResults(p1_0.05_p2_0.05_p3_0.5_p4_0.5)
plotResults(p1_0.05_p2_0.05_p3_0_p4_1)
plotResults(p1_0.05_p2_0.05_p3_1_p4_0)
```

# Round 2: 5 simulations, 1000 permutations per simulation

```{r sim2, echo=FALSE, message=FALSE}
rm(list=ls())

source("./code/plotResults.R")

newResults <- grep("noidr", grep("p4", list.files("./data"), value=T), invert=T, value=T)
for(x in newResults) { load(paste0("./data/", x)) }

# load results files
resultsFiles <- grep("noidr", list.files("./data"), value=T)
for(x in resultsFiles) { load(paste0("./data/", x)) }
```

Parameters: 

* proportion differentially expressed in drug signature (p1): 0.05
* proportion differentially expressed in disease signature (p2): 0.05
* proportion differentially expressed in same direction (p3): 0, 0.5, 1
* proportion differentially expressed in different direction (p4): 0, 0.5, 1

Statistics: GSEA, Spearman correlation, truncated Spearman correlation

Figure legends:

* Blue histogram: permutation statistics

* Red dots: simulation statistics

* Green violin plots: simulation p-values

```{r sim2Plots, echo=FALSE, message=FALSE, fig.cap=""}
plotResults(p1_0.05_p2_0.05_p3_0_p4_0)
plotResults(p1_0.05_p2_0.05_p3_0_p4_0.5)
plotResults(p1_0.05_p2_0.05_p3_0.5_p4_0)
# plotResults(p1_0.05_p2_0.05_p3_0.5_p4_0.5)
# plotResults(p1_0.05_p2_0.05_p3_0_p4_1)
# plotResults(p1_0.05_p2_0.05_p3_1_p4_0)
```
